PoolTestRPaper

### 2020-10-19 paper/Paper.Rmd
Generalise getPrevalence and Prepare for CRAN submission

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.extra = R.version.string)
knitr::opts_chunk$set(cache.extra = R.version)
library(PoolTestR)
```

@@

# Fit a Bayesian model
HierPrevModel <- PoolRegBayes(Result ~ Region + (1|Village/Site), Data, PoolSize)
# Extracting  prevalence at each level from the fitted model. The output is a list with three entries:
#     Prevalence for each combination of population effects (in this case this is region)
#     Prevalence for each Village within each region
#     Prevalence for each site within each village and region
HierPrevs <- getPrevalence(HierPrevModel) 
head(HierPrevs)

@@

```
```{r HierComparisonVillage, echo=FALSE, warning = FALSE}
PlotDataVillage <- PrevVillage %>%
  unique %>%
  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevVillage %>%
              unique %>%
              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region, Village,PrevalenceVillage) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceVillage)) %>%
  bind_rows(HierPrevs$Village %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
  subset(VillageNum %in% 1:5)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.extra = R.version.string)
knitr::opts_chunk$set(cache.extra = R.version)
library(PoolTestR)
library(dplyr)
```

@@

# Fit a Bayesian model
HierPrevModel <- PoolRegBayes(Result ~ Region + (1|Village/Site), Data, PoolSize)
# Extracting  prevalence at each level from the fitted model. The output is a list with three entries:
#     Prevalence for each combination of population effects (in this case this is region)
#     Prevalence for each Village within each region
#     Prevalence for each site within each village and region
HierPrevs <- getPrevalence(HierPrevModel)

@@

```{r PrevByVillage, include=FALSE, cache=TRUE}
PrevVillage <- PoolPrev(Data, Result, PoolSize, Region, Village)
```

```{r HierComparisonVillage, echo=FALSE, warning = FALSE}
PlotDataVillage <- PrevVillage %>%
  unique %>%
  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevVillage %>%
              unique %>%
              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region, Village,PrevalenceVillage) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceVillage)) %>%
  bind_rows(HierPrevs$Village %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
  subset(VillageNum %in% 1:5)
